Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-15 Tex/Old text/chapters/chapter02.tex
Thesis update

In this chapter some concepts related to the intersection of the two areas of this research are presented: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.

First, the concept of formal verification is introduced as background to understanding how a methodology that performs (mainly) bug detection can be used to validate a design sizing or to obtain an optimal solution of PV systems.

@@

Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.

@@

At this work will be evaluated three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t. user requirements.

@@

@@

ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

@@

\section{Solar Photovoltaic System }
According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time (in particular cases, in both times). The most basic PV system can give supply only in daytime.  For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.

>>>>

In this chapter we present some concepts related to the intersection of the two areas: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.

First, we introduce the concept of formal verification as background to understanding how a methodology that performs (mainly) bug detection can be used to validate a design sizing or to obtain an optimal solution of PV systems.

@@

Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. In other words, the problem is not dealing with an abstraction of the actual system under study.

@@

At this work we will evaluated three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t. user requirements. Moreover, different solvers will be evaluated as well, according with the feature of each model checker.

@@

Particularly, CBMC comes with a built-in solver for bit-vector formulas that is based on MiniSat. We used this solver during the experimentation in this PhD thesis~\cite{Kroening}.

@@

ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state. ESBMC in 'incremental SMT' uses only Z3 solver~\cite{DeMoura}.

@@

Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}. Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do. The specification needs to describe the program's desired behavior to ensure that the program does what it intends.

@@

\section{Solar Photovoltaic System }

According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time (in particular cases, in both times). The most basic PV system can give supply only in daytime.  For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.

### 2019-10-15 Tex/Old text/chapters/chapter03.tex
revised Chapter 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
Thesis update

%\section{Introduction}
%
In this Chapter, the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking, will be detailed. Diagrams, flowcharts, and algorithms support and explain the solutions.

Besides that, all the assumptions and premises adopted are presented. Both support the results/conclusions, with direct impact on it. Usually, a premise is an unquestionable fact, however assumptions can be questionable. Unlike the premise, assumptions are not explicitly stated and need to be deciphered. With that in mind, a detailed explanation of assumptions is performed for all over this Chapter.

It is important to emphasize that the whole explanation about the theoretical basis of the two subjects discussed here are present in the previous chapter. In addition, the author suggests that previous reading be done to facilitate understanding.

>>>>

%\textcolor{red}{This title ``Methodology'' is too generic!!! methodology of what?}
%
%\section{Introduction}
%
In this Chapter, we detail the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking. Diagrams, flowcharts, and algorithms support and explain the solutions.

Besides that, we present all the assumptions and premises adopted. Both support the results/conclusions, with direct impact on it. Usually, a premise is an unquestionable fact, however assumptions can be questionable. Unlike the premise, assumptions are not explicitly stated and need to be deciphered. With that in mind, we perform a detailed explanation of assumptions all over this Chapter.

It is important to emphasize that the whole explanation about the theoretical basis of the two subjects discussed here are present in the previous chapter. In addition, we do suggest that previous reading must be done to facilitate the understanding.
